---
title: "goSWATplus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{goSWATplus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(goSWATplus)
```

# Initial SWAT+ Simulation

First, you can download a light demo project from the `SWATplusR` package. Per the introduction to `SWATplusR`,
run the following code to download the demo. See https://chrisschuerz.github.io/SWATplusR/articles/SWATplusR.html 
for additional detail.

## Download demo data

```{r}
# The path where the SWAT demo project will be written
demo_path <- "C:/Users/gopenny/Documents/SWAT models/SWATplusR_demos"
demo_path <- "Define:/your/path"

# Loading a SWAT+ demo project
path_plus <- SWATplusR::load_demo(dataset = "project",
                                  version = "plus",
                                  path = demo_path,
                                  revision = 57)
```

## Run demo simulation

The demo can be run exclusively using `SWATplusR` package, with the `run_swatplus` command which prepares the simulation, generates calibration files, runs SWAT in a temporary folder, and read the results to R. Alternatively, the `goSWATplus` package allows you to separate different aspects of the simulation and run the swatplus executable directly in the existing folder. To run the demo using `goSWATplus`, execute the following code:

```{r}
demo_path_57 <- "C:/Users/gopenny/Documents/SWAT models/SWATplusR_demos/swatplus_rev57_demo"
run_swat(demo_path_57)
```

The function above, `run_swat`, identifies executable files in the specified path and simply
runs the first one from the command line. Because the application is run in place,
files within the directory are directly modified and written to.


